---
title: "EpitoScope report"
runtime: shiny
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: united
    number_sections: true
    self_contained: true
    fig_width: 12
    fig_height: 6
params:
  data_info: NULL
  data_list: NULL
  processed_data_list: NULL
---

<style>
/* Remove bootstrap offsets so TOC can be at absolute left */
.container-fluid,
.container,
.row-fluid {
  padding-left: 0 !important;
  margin-left: 0 !important;
  padding-right: 0 !important;
  margin-right: 0 !important;
}

/* Left TOC */
#toc {
  position: fixed !important;
  top: 80px !important;
  left: 0 !important;
  width: 160px !important;
  background: #f8f8f8;
  border-right: 1px solid #ddd;
  padding: 10px !important;
  margin: 0 !important;
  max-height: calc(100% - 100px);
  overflow-y: auto;
}

.tocify-wrapper {
    width: 200px;   /* default might be 250-300px */
}

/* Main content shifted right of TOC */
.main-container {
  margin-left: 180px !important; /* slightly bigger than TOC width */
  padding: 20px !important;
  width: calc(100% - 180px) !important;
  max-width: none !important;
  box-sizing: border-box !important;
}

/* Figures full width */
figure, img, .plot-container, .html-widget {
  width: 100% !important;
  max-width: 100% !important;
}

@media (max-width: 900px) {
  #toc {
    position: relative !important;
    width: 100% !important;
    margin: 0 !important;
    border-right: none !important;
  }
  .main-container {
    margin-left: 0 !important;
    width: 100% !important;
  }
}
</style>

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(ggpointdensity)
library(viridis)
library(purrr)
library(shiny)
library(plotly)
library(ComplexUpset)
library(GGally)
library(ggrepel)
source("global.R")

data_info <- params$data_info
data_list <- params$data_list
processed_list <- params$processed_data_list
```

# RAW Summary {.tabset}

## Column Map

```{r}
Colum_mapping_table(data_info)
```

## Unique Entries {.tabset}

### Peptides

```{r}
plot_unique_counts(data_list, column = "STRIPPED", y_label = "Number of unique peptides")
```

### Peptidoforms

```{r}
plot_unique_counts(data_list, column = "PEPTIDE", y_label = "Number of unique peptidoforms")
```

### Proteins

```{r}
plot_unique_counts(data_list, column = "PROTEIN", y_label = "Number of unique proteins",
                       transform_fn = extract_protein_prefixes)
```

## Other Numeric Columns {.tabset}

### Charge

```{r}
plot_stacked_bar(data_list, column = "CHARGE", fill_label = "Charge", percentage = FALSE)
```

### Mass

```{r}
plot_density(data_list, column = "MASS", x_label = "Mass (Da)")
```

### m/z

```{r}
plot_density(data_list, column = "MZ", x_label = "m/z")
```

### Retention Time

```{r}
plot_density(data_list, column = "RT", x_label = "Retention Time (min)")
```

### ppm

```{r}
plot_density(data_list, column = "PPM", x_label = "ppm")
```

### Score

```{r}
plot_violin(data_list, column = "SCORE")
```

## Summary Table

```{r}
render_summary_pre(data_list, font_size = "8px")
```

# QC {.tabset}

## Peptide Length Distribution

```{r}
plot_length_distribution(processed_list)
```

## Motif Plot {.tabset}

```{r motif_grid, echo=FALSE, message=FALSE, warning=FALSE}
library(patchwork)

lst <- params$lst

# Generate scatterplots
scatter_list <- generate_scatterplots(lst)

if (length(scatter_list) == 0) {
  # Show placeholder if no plots available
  print(
    ggplot() +
      annotate("text", x = 0.5, y = 0.5,
               label = "No scatterplots available",
               size = 6, color = "red") +
      theme_void()
  )
} else {
  # Combine all plots in a grid
  grid_plot <- wrap_plots(scatter_list, ncol = 2)
  print(grid_plot)
}
```
## Dynamic Range {.tabset}

### Individual

```{r dynrange_grid, echo=FALSE, message=FALSE, warning=FALSE}
library(patchwork)

lst <- params$lst

# Generate plots per sample
dynrange_list <- generate_dynrange_grid(lst)

# Remove NULL/empty plots if any
dynrange_list <- Filter(function(p) !is.null(p), dynrange_list)

if (length(dynrange_list) == 0) {
  # Show placeholder if no plots available
  print(
    ggplot() +
      annotate("text", x = 0.5, y = 0.5,
               label = "Not enough peptides for any sample",
               size = 6, color = "red") +
      theme_void()
  )
} else {
  # Combine all plots in a grid (e.g., 2 per row)
  grid_plot <- wrap_plots(dynrange_list, ncol = 2)
  print(grid_plot)
}
```

### Combined

```{r}
dynamic_range_plot_combined(df_list = lst, data_col = "MAX_QUANTITY")
```

## 1/k0 vs m/z
```{r k0_vs_mz_grid, echo=FALSE, message=FALSE, warning=FALSE}
library(patchwork)

lst <- params$lst

# Generate scatterplots
scatter_list <- generate_scatterplots(lst)

# Remove NULL/empty plots if any
scatter_list <- Filter(function(p) !is.null(p), scatter_list)

if (length(scatter_list) == 0) {
  print(
    ggplot() +
      annotate("text", x = 0.5, y = 0.5,
               label = "No scatterplots available",
               size = 6, color = "red") +
      theme_void()
  )
} else {
  # Combine all plots in a grid
  grid_plot <- wrap_plots(scatter_list, ncol = 2)
  print(grid_plot)
}
```

# Results {.tabset}

## Data Completeness {.tabset}

### Absolute

```{r}
plot_completeness(processed_list)
```

### Percentage

```{r}
plot_completeness(processed_list, percent = TRUE)
```

## Upset Plot of Peptides

```{r}
plot_upset(processed_list)
```

## Pairwise Overlap Matrix

```{r}
plot_shared_peptide_matrix(processed_list)
```

## Unique Entries (Processed) {.tabset}

### Peptides

```{r}
plot_unique_counts(processed_list, column = "STRIPPED", y_label = "Number of unique peptides")
```

### Peptidoforms

```{r}
plot_unique_counts(processed_list, column = "PEPTIDE", y_label = "Number of unique peptidoforms")
```

### Proteins

```{r}
plot_unique_counts(processed_list, column = "PROTEIN", y_label = "Number of unique proteins",
                       transform_fn = extract_protein_prefixes)
```

## Other Numeric Columns {.tabset}

### Charge

```{r}
plot_stacked_bar(processed_list, column = "CHARGE", fill_label = "Charge", percentage = FALSE)
```

### Mass

```{r}
plot_density(processed_list, column = "MASS", x_label = "Mass (Da)")
```

### m/z

```{r}
plot_density(processed_list, column = "MZ", x_label = "m/z")
```

### Retention Time

```{r}
plot_density(processed_list, column = "RT", x_label = "Retention Time (min)")
```

### ppm

```{r}
plot_density(processed_list, column = "PPM", x_label = "ppm")
```

### Score

```{r}
plot_violin(processed_list, column = "SCORE")
```