---
title: "EpitoScope Report"
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    theme: flatly        # closest Bootstrap 3 theme to AdminLTE3's clean look
    highlight: textmate
    number_sections: true
    self_contained: true
    fig_width: 12
    fig_height: 6
params:
  data_info:           NULL
  data_list:           NULL
  data_mod_map:        NULL
  mod_map_list:        NULL
  processed_data_list: NULL
  filters:             NULL
  color_palette:       "default"
  cluster_mode_ea:     "sample"
  binder_summary_all:  NULL
  binder_unique:       NULL
  group_list:          NULL
  group_comp_data:     NULL
  annotation_table:    NULL
---

<style>
/* ── AdminLTE3 / bs4Dash colour tokens ─────────────────────────────────── */
/* Primary blue  : #3c8dbc  (AdminLTE default)                              */
/* Sidebar dark  : #343a40                                                  */
/* Body bg       : #f4f6f9                                                  */
/* Card bg       : #ffffff                                                  */
/* Card border   : #dee2e6 / top accent strip matches card status colour    */
/* Accent (info) : #17a2b8                                                  */

/* ── Fonts ─────────────────────────────────────────────────────────────── */
body {
  font-family: 'Source Sans Pro', 'Helvetica Neue', Helvetica, Arial, sans-serif;
  font-size: 14px;
  color: #212529;
  background-color: #f4f6f9;  /* AdminLTE body bg */
}

/* ── Page title block ──────────────────────────────────────────────────── */
h1.title {
  font-size: 24px;
  font-weight: 600;
  color: #343a40;
  border-bottom: 3px solid #3c8dbc;
  padding-bottom: 8px;
  margin-bottom: 4px;
}

h4.date {
  font-size: 12px;
  color: #6c757d;
  font-weight: 400;
  margin-top: 2px;
}

/* ── Section headings  ─────────────────────────────────────────────────── */
h1 { font-size: 20px; font-weight: 600; color: #343a40;
     border-bottom: 2px solid #dee2e6; padding-bottom: 5px; }
h2 { font-size: 16px; font-weight: 600; color: #495057; }
h3 { font-size: 14px; font-weight: 600; color: #6c757d; }

/* ── TOC — mirrors bs4Dash sidebar ────────────────────────────────────── */
#TOC {
  background-color: #343a40;  /* AdminLTE sidebar dark */
  border-right: none;
  padding: 14px 10px;
  font-size: 12.5px;
  color: #c2c7d0;
  border-radius: 0 4px 4px 0;
}

.tocify-header > .tocify-item > a,
.tocify-subheader > .tocify-item > a {
  color: #c2c7d0 !important;
  padding: 5px 10px;
  display: block;
}

.tocify-header > .tocify-item > a:hover,
.tocify-subheader > .tocify-item > a:hover {
  color: #ffffff !important;
  background-color: #3c8dbc !important;
  border-radius: 3px;
}

.tocify .list-group-item.active,
.tocify .list-group-item.active:hover {
  background-color: #3c8dbc !important;
  border-color:     #3c8dbc !important;
  color: #ffffff !important;
  border-radius: 3px;
}

/* ── Main content ──────────────────────────────────────────────────────── */
.main-container {
  max-width: none !important;
  padding: 20px 28px;
  background-color: #f4f6f9;
}

/* ── Section cards ─────────────────────────────────────────────────────── */

/* Level 1 (e.g. # RAW Summary) — card with stronger accent */
.section.level1 {
  background:    #ffffff;
  border:        1px solid #dee2e6;
  border-top:    3px solid #3c8dbc;
  border-radius: 4px;
  padding:       0px 10px;
  margin-bottom: 24px;
  box-shadow:    0 1px 4px rgba(0,0,0,0.07);
}

/* Level 2 (e.g. ## Column Map) — just a divider, no box */
.section.level2 {
  background:  transparent;
  border:      none;
  border-bottom: 1px solid #f0f0f0;
  border-radius: 0;
  padding:     8px 0 16px 0;
  margin-bottom: 8px;
  box-shadow:  none;
}

/* Level 3 (e.g. ### Peptides inside a tabset) — no box, just spacing */
.section.level3 {
  background:  transparent;
  border:      none;
  padding:     8px 0;
  margin:      0;
  box-shadow:  none;
}

/* ── Tabs — AdminLTE nav-tabs ──────────────────────────────────────────── */
.nav-tabs {
  border-bottom: 2px solid #dee2e6;
  margin-bottom: 0;
}

.nav-tabs > li > a {
  color: #495057;
  font-size: 13px;
  font-weight: 500;
  border: 1px solid transparent;
  border-radius: 3px 3px 0 0;
  padding: 6px 14px;
}

.nav-tabs > li > a:hover {
  background-color: #f8f9fa;
  border-color: #dee2e6 #dee2e6 transparent;
}

.nav-tabs > li.active > a,
.nav-tabs > li.active > a:hover,
.nav-tabs > li.active > a:focus {
  color:            #3c8dbc;
  background-color: #ffffff;
  border-color:     #dee2e6 #dee2e6 #ffffff;
  border-top:       2px solid #3c8dbc;
  font-weight:      600;
}

.tab-content {
  background:    #ffffff;
  border:        1px solid #dee2e6;
  border-top:    none;
  border-radius: 0 0 4px 4px;
  padding:       18px;
  margin-bottom: 16px;
}

/* ── Tables ────────────────────────────────────────────────────────────── */
table {
  font-size: 13px;
  width: 100%;
  border-collapse: collapse;
}

thead tr {
  background-color: #3c8dbc;
  color: #ffffff;
}

thead th {
  padding: 8px 10px;
  font-weight: 600;
}

tbody tr:nth-child(even) { background-color: #f8f9fa; }
tbody tr:hover           { background-color: #e8f4f8; }

tbody td { padding: 6px 10px; }

/* ── Figures ───────────────────────────────────────────────────────────── */
figure, img, .plot-container, .html-widget {
  width: 100% !important;
  max-width: 100% !important;
}

/* ── Code / pre ────────────────────────────────────────────────────────── */
pre, code {
  font-family: 'SFMono-Regular', Consolas, 'Liberation Mono', Menlo, monospace;
  font-size: 12px;
}

pre {
  background:    #f8f9fa;
  border:        1px solid #dee2e6;
  border-radius: 3px;
  padding:       10px 14px;
}

/* ── Responsive ────────────────────────────────────────────────────────── */
@media (max-width: 900px) {
  #TOC            { background-color: #f8f9fa; color: #212529; border-right: 1px solid #dee2e6; }
  .main-container { padding: 12px; }
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE
)

source("global.R")

data_info      <- params$data_info
data_list      <- params$data_list
mod_map_list   <- params$mod_map_list
processed_list <- params$processed_data_list
cluster_mode_ea <- params$cluster_mode_ea
color_palette   <- params$color_palette
binder_summary_all <- params$binder_summary_all
binder_unique   <- params$binder_unique
group_list      <- params$group_list
group_comp_stats <- params$group_comp_data
min_presence_fraction <- params$filters$min_presence_fraction
data_mod_map <- params$data_mod_map
annotation_table <- params$annotation_table

motif_plot_length <- 7:13 # should be the same as in Shiny.R
```

# Settings and Documentation {.tabset}

## Column Map

```{r}
DT::datatable(
  Colum_mapping_table(data_info),
  escape   = FALSE,   # <-- this is the key, allows the HTML spans to render
  options  = list(pageLength = 20, scrollX = TRUE, autoWidth = TRUE),
  rownames = FALSE
)
```

## Annotation Table

```{r}
if (!is.null(annotation_table)) {
  DT::datatable(annotation_table)
} else {
  cat("No annotation table was provided.")
}
```

## Analysis Parameters

```{r filter_summary, results='asis'}
f <- params$filters

make_row <- function(label, val) {
  if (is.null(val)) return(NULL)
  if (length(val) == 2 && is.numeric(val)) {
    formatted <- paste0(round(val[1], 2), " – ", round(val[2], 2))
  } else {
    formatted <- paste(val, collapse = ", ")
  }
  data.frame(Parameter = label, Value = formatted, stringsAsFactors = FALSE)
}

filter_df <- do.call(rbind, Filter(Negate(is.null), list(
  make_row("Samples",        f$samples),
  make_row("Length range",   f$length_range),
  make_row("Quantity range", f$quantity_range),
  make_row("Score range",    f$score_range),
  make_row("Charge range",   f$charge_range),
  make_row("Mass range",     f$mass_range),
  make_row("RT range",       f$RT_range),
  make_row("min_presence_fraction",       f$min_presence_fraction)
)))

knitr::kable(filter_df, row.names = FALSE)
```

# RAW Summary {.tabset}

## Unique Entries {.tabset}

### Peptides

```{r}
plot_unique_counts(data_list, column = "STRIPPED", y_label = "Number of unique peptides", color = color_palette)
```

### Peptidoforms

```{r}
plot_unique_counts(data_list, column = "PEPTIDE", y_label = "Number of unique peptidoforms", color = color_palette)
```

### Proteins

```{r}
plot_unique_counts(data_list, column = "PROTEIN", y_label = "Number of unique proteins",
                   transform_fn = extract_protein_prefixes, color = color_palette)
```

## Other Numeric Columns {.tabset}

### Charge

```{r}
plot_stacked_bar(data_list, column = "CHARGE", fill_label = "Charge", percentage = FALSE, color = color_palette)
```

### Mass

```{r}
plot_density(data_list, column = "MASS", x_label = "Mass (Da)", color = color_palette)
```

### m/z

```{r}
plot_density(data_list, column = "MZ", x_label = "m/z", color = color_palette)
```

### Retention Time

```{r}
plot_per_sample_grid(
  lst      = data_list,
  plot_fn  = plot_histogram,
  ncol     = 2,
  column   = "RT",
  x_label  = "Retention Time (min)",
  color    = color_palette
)
```

### ppm

```{r}
plot_density(data_list, column = "PPM", x_label = "ppm", color = color_palette)
```

### Score

```{r}
plot_violin(data_list, column = "SCORE", color = color_palette)
```

## Summary Table

```{r}
render_summary_pre(data_list, font_size = "8px")
```

# QC {.tabset}

## Peptide Length Distribution

```{r}
plot_length_distribution(processed_list, color = color_palette)
```

## Peptide Length Distribution

```{r}
    lst <- lapply(processed_list, function(df) {
      df$correct_range <- df$LENGTH >= 8 & df$LENGTH <= 13
      df
    })
plot_stacked_bar(lst, column = "correct_range", fill_label = "8-13mer", percentage = TRUE, color = color_palette)
```

## Motif Plot

```{r motif, fig.height = length(motif_plot_length) * 3}
plot_motif_grid(
  lst     = processed_list,
  lengths = motif_plot_length,
  ncol    = length(processed_list)
)
```

## Dynamic Range {.tabset}

### Individual

```{r}
plot_per_sample_grid(
  lst      = processed_list,
  plot_fn  = dynamic_range_plot,
  ncol     = 2,
  data_col = "MAX_QUANTITY",
  name_col = "PROTEIN",
  gene     = "HLA",
  gene_regex = "HLA[A-C]+"
)
```

### Combined

```{r dynrange_combined}
dynamic_range_plot_combined(df_list = processed_list, data_col = "MAX_QUANTITY")
```

## 1/k0 vs m/z

```{r k0_vs_mz_grid, fig.height=5}
scatter_list <- generate_scatterplots(processed_list)
scatter_list <- Filter(Negate(is.null), scatter_list)

if (length(scatter_list) == 0) {
  ggplot() + annotate("text", x=.5, y=.5, label="No scatterplots available", size=6, color="red") + theme_void()
} else {
  wrap_plots(scatter_list, ncol = min(2, length(scatter_list)))
}
```

## Measurement Correlation Heatmap
````{r measurement_heatmap}
quantity_cols <- data_info %>%
  filter(final_name == "QUANTITY") %>%
  dplyr::select(-final_name) %>%
  unlist(recursive = TRUE, use.names = FALSE)

if (length(quantity_cols) == 0) {
  cat("No QUANTITY columns found.")
} else {
  pep_mat <- prepare_measurement_matrix(processed_list, quantity_cols)
  
  if (ncol(pep_mat) < 2 || nrow(pep_mat) == 0) {
    cat("_Not enough data to compute correlation.")
  } else {
    
    cor_mat <- cor(pep_mat, method = "pearson", use = "complete.obs")
    
    group_names <- names(lst)

    get_group <- function(colname) {
      matched <- group_names[sapply(group_names, function(g) startsWith(colname, g))]
      if (length(matched) == 0) return(NA)
      matched[1]
    }
    
    if (cluster_mode_ea == "sample") {
      groups <- sapply(colnames(cor_mat), get_group)
      ht <- plot_heatmap(cor_mat, color = color_palette,
                         row_groups = groups, col_groups = groups, label = "Pearson")
    } else if (cluster_mode_ea == "mix") {
      col_groups <- sapply(colnames(cor_mat), get_group)
      ht <- plot_heatmap(cor_mat, color = color_palette, cluster = "rows",
                         row_groups = NULL, col_groups = col_groups, label = "Pearson")
    } else {
      ht <- plot_heatmap(cor_mat, color = color_palette,
                         cluster = cluster_mode_ea, label = "Pearson")
    }
    
    pad <- compute_padding(colnames(cor_mat), fontsize = 10, rot = 90)
    
    draw(ht,
         heatmap_legend_side = "left",
         padding = unit.c(
           unit(pad / 2, "mm"),
           unit(2,       "mm"),
           unit(2,       "mm"),
           unit(pad,     "mm")
         )
    )
  }
}

````

# Results {.tabset}

## Data Completeness {.tabset}

### Absolute

```{r}
spectra_cols <- data_info %>%
  filter(final_name == "SPECTRA") %>%
  dplyr::select(-final_name) %>%
  unlist(use.names = FALSE)

plot_completeness(processed_list, spectra_cols, color = color_palette)
```

### Percentage

```{r}
plot_completeness(processed_list, spectra_cols, percent = TRUE, color = color_palette)
```

## Upset Plot

```{r}
plot_upset(processed_list)
```

## Pairwise Overlap Matrix {.tabset}

### Count

```{r}
plot_shared_peptide(processed_list, mode = "count", percent_type = "union", color = color_palette)
```

### Percent

```{r}
plot_shared_peptide(processed_list, mode = "percent", percent_type = "union", color = color_palette)
```

## Pairwise comparison Matrix {.tabset}

### No cluster

```{r}
plot_pairwise_peptide_quant_correlation(processed_list, color = color_palette, cluster = "none")
```

### Cluster

```{r}
plot_pairwise_peptide_quant_correlation(processed_list, color = color_palette, cluster = "both")
```

## PCA plot

```{r}
plot_PCA(processed_list, color = color_palette)
```


## Unique Entries (Filtered) {.tabset}

### Peptides

```{r}
plot_unique_counts(processed_list, column = "STRIPPED", y_label = "Number of unique peptides", color = color_palette)
```

### Peptidoforms

```{r}
plot_unique_counts(processed_list, column = "PEPTIDE", y_label = "Number of unique peptidoforms", color = color_palette)
```

### Proteins

```{r}
plot_unique_counts(processed_list, column = "PROTEIN", y_label = "Number of unique proteins",
                   transform_fn = extract_protein_prefixes, color = color_palette)
```

## Other Numeric Columns {.tabset}

### Charge

```{r}
plot_stacked_bar(processed_list, column = "CHARGE", fill_label = "Charge", percentage = FALSE, color = color_palette)
```

### Mass

```{r}
plot_density(processed_list, column = "MASS", x_label = "Mass (Da)", color = color_palette)
```

### m/z

```{r}
plot_density(processed_list, column = "MZ", x_label = "m/z", color = color_palette)
```

### Retention Time

```{r}
plot_per_sample_grid(
  lst      = processed_list,
  plot_fn  = plot_histogram,
  ncol     = 2,
  column   = "RT",
  x_label  = "Retention Time (min)",
  color    = color_palette
)
```

### ppm

```{r}
plot_density(processed_list, column = "PPM", x_label = "ppm", color = color_palette)
```

### Score

```{r}
plot_violin(processed_list, column = "SCORE", color = color_palette)
```

# Groups {.tabset}

## Group based Venn Diagram

```{r}
if (!is.null(group_list)) {
  lst <- processed_list
  groups <- group_list
  pep_col <- "PEPTIDE"
  #pep_col    <- if (!is.null(input$use_peptidoforms) && input$use_peptidoforms) "PEPTIDE" else "STRIPPED"
  
  group_peptide_sets <- lapply(names(groups), function(g) {
      
      sample_names <- groups[[g]]
      
      peptide_counts <- table(unlist(lapply(sample_names, function(s) {
        df <- lst[[s]]
        if (!pep_col %in% colnames(df)) return(character(0))
        unique(df[[pep_col]])
      })))
      
      n_samples <- length(sample_names)
      
      names(peptide_counts[
        peptide_counts / n_samples >= min_presence_fraction
      ])
    }) |> setNames(names(groups))
  
  
  group_venn_plotting(group_peptide_sets, color = color_palette)
} else {
  cat("no Groups defined")
}
```

## Peptide based Heatmap

```{r}
if (!is.null(group_list)) {
    lst <- processed_list
    groups <- group_list
    
    quantity_cols <- data_info %>%
      filter(final_name == "QUANTITY") %>%
      dplyr::select(-final_name) %>% 
      unlist(recursive = TRUE, use.names = FALSE)
    
    if(length(quantity_cols) < 1) {
      cat("No QUANTITY columns found.")
      return(NULL)
    }
    
    pep_mat <- prepare_peptide_matrix(lst, groups, quantity_cols, group_peptide_sets)
    
    if(nrow(pep_mat)  < 1) {
      cat("No peptides to plot.")
      return(NULL)
    }
    
    plot_heatmap(pep_mat, color = color_palette, transpose = TRUE, log_transform = TRUE)
} else {
  cat("no Groups defined")
}
```

## Group Comparison {.tabset}

```{r group_comp, results='asis', fig.height=5}
if (is.null(group_comp_stats) || length(group_comp_stats) == 0) {
  cat("_No group comparison data available._\n")
} else {

  for (comp_name in names(group_comp_stats)) {
    df <- group_comp_stats[[comp_name]]

    df$Significance <- ifelse(
      is.na(df$negLog10AdjP_BH) | is.na(df$log2FC), "Missing",
      ifelse(df$negLog10AdjP_BH > 1.3 & abs(df$log2FC) > 1,
             "Significant", "Not significant")
    )

    if (is.null(df) || nrow(df) == 0) next

    # Tab header — must be followed by a blank line
    cat("\n\n###", comp_name, "\n\n")

    # Volcano + MA
    p <- patchwork::wrap_plots(
      group_volcano_plot_static(df, comp_name),
      group_MA_plot_static(df, comp_name),
      ncol = 2
    )
    print(p)
    cat("\n\n")

    # P-value histogram + Ranked FC
    p2 <- patchwork::wrap_plots(
      group_p_histogram_static(df, comp_name),
      group_rank_FC_static(df, comp_name),
      ncol = 2
    )
    print(p2)
    cat("\n\n")

    # Peptide table — knit_print renders htmlwidgets inline in results='asis'
    table_df <- df %>%
      filter(!is.na(log2FC)) %>%
      dplyr::select(PEPTIDE, log2FC, adj_pval_BH, adj_pval_Bonf, Significance) %>%
      arrange(adj_pval_BH)

    
    cat(knitr::knit_print(
      DT::datatable(
        table_df,
        rownames = FALSE,
        caption  = paste("Differential peptides —", comp_name),
        options  = list(pageLength = 10, scrollX = TRUE)
      ) %>% DT::formatRound(c("log2FC", "adj_pval_BH", "adj_pval_Bonf"), digits = 3)
    ))
    
    cat("\n\n")

    # GO term
    cat("\n\n#### GO-term enrichment\n\n")
    res <- run_go_enrichment(df)
    if (is.list(res) && isTRUE(res$.skip)) {
      cat(res$message, "\n\n")
    } else {
      print(res)
      cat("\n\n")
    }

    # STRING
    cat("\n\n#### STRING-DB network\n\n")
    if (!curl::has_internet()) {
      cat("_No internet connection — STRING-DB network unavailable._\n\n")
    } else {
      res <- run_string(df)
      if (is.list(res) && isTRUE(res$.skip)) {
        cat(res$message, "\n\n")
      } else {
        print(res)
        cat("\n\n")
      }
    }
  }
}
```

# PTM {.tabset}

## PTM distribution

```{r}
has_ptm <- sapply(processed_list, function(df) "PTM" %in% colnames(df))

if (!any(has_ptm)) {
  cat("No PTM column found in any dataset.")
} else {
  
  lst <- processed_list[has_ptm]  # only keep samples that have PTM
  
  lst <- lapply(lst, function(df) {
    df %>%
      mutate(
        PTM = ifelse(is.na(PTM) | PTM == "", "Unmodified", PTM)
      ) %>%
      tidyr::separate_rows(PTM, sep = "\\s*[,;]\\s*") %>%
      mutate(
        PTM = gsub("^\\d+", "", PTM)
      )
  })
  
  plot_stacked_bar(lst, column = "PTM", fill_label = "PTM", 
                   percentage = FALSE, rev_levels = FALSE)
}
```

## PTM sequence motif

```{r}
if (is.null(mod_map_list) || length(mod_map_list) == 0 || all(is.na(mod_map_list))) {
      cat("no PTM pseudo sequence")
} else {
          # Flatten the list into a single data.frame
    mod_map_list <- purrr::imap_dfr(mod_map_list, ~ tibble(
      Sample = .y,
      Symbol = .x,
      Modification = names(.x)
    ))
    
    DT::datatable(mod_map_list, options = list(pageLength = 20))
    }
    

```

```{r ptm_motif, results='asis'}
ptm_mod_map <- data_mod_map

if (is.null(ptm_mod_map) || length(ptm_mod_map) == 0 || all(is.na(ptm_mod_map))) {
  cat("_No PTM pseudo sequence available._\n")
} else {
  AA_symbols  <- LETTERS
  PTM_symbols <- c(as.character(1:9), letters)
  namespace   <- c(AA_symbols, PTM_symbols)
  
  print(
    plot_motif_grid(
      lst       = processed_list,
      lengths   = motif_plot_length,
      ncol      = length(processed_list),
      ptm_only  = TRUE,
      namespace = namespace
    )
  )
}
```

# Binding {.tabset}

WIP: For speed sake, binder data is directly obtained rather than recalculated. As such, it needs to reactively update for the updated data to make it to this report.

## Binding Summary

```{r}
if (!is.null(binder_summary_all)) {
  DT::datatable(binder_summary_all)
} else {
  cat("no binding data")
}
```

## Summary Barchart {.tabset}

### Absolute

```{r}
if (!is.null(binder_unique)) {
  plot_binders(binder_unique, color = color_palette, percent = FALSE)
} else {
  cat("no binding data")
}
```

### Percent

```{r}
if (!is.null(binder_unique)) {
  plot_binders(binder_unique, color = color_palette, percent = TRUE)
} else {
  cat("no binding data")
}
```

## Binding Table

```{r}
if (!is.null(binder_unique)) {
  
      df_collapsed <- binder_unique %>%
      group_by(STRIPPED) %>%
      summarise_all(~ {
        vals <- unique(.)
        vals <- vals[!is.na(vals)]
        if(length(vals) == 0) NA else paste(vals, collapse = ",")
      })
  
  DT::datatable(df_collapsed)
} else {
  cat("no binding data")
}
```

# Lookup
For unique peptides per sample, set n_datasets = 1
```{r}
keep_cols <- c("Sample", "PEPTIDE", "STRIPPED", "MAX_QUANTITY","LENGTH" ,"MASS" ,"CHARGE", "MZ" ,"K0", "RT", "PROTEIN")
    
combined <- imap_dfr(data_list, ~ dplyr::select(.x, intersect(keep_cols, colnames(.x))) %>% mutate(Sample = .y))
    
peptide_counts <- combined %>% distinct(STRIPPED, Sample) %>% count(STRIPPED, name = "n_datasets")
    
numeric_cols <- c("LENGTH", "MASS", "CHARGE", "MZ", "K0", "RT")
    
combined <- combined %>% inner_join(peptide_counts, by = "STRIPPED") %>%
  arrange(Sample, STRIPPED) %>%
  mutate(across(any_of(numeric_cols), as.numeric))

combined <- combined[,c(1,2,3,4,5,6,7,8,9,11,12,10)]

DT::datatable(
  combined,
  filter   = "top",
  rownames = FALSE,
  options  = list(
    pageLength  = 25,
    scrollX     = TRUE,
    dom         = "frtip",
    autoWidth   = FALSE,
    initComplete = JS("function(settings, json) { this.api().columns.adjust(); }")
  )
)
```



